Hydra Battles and Cie

### 2021-08-27 doc/hydras.tex
re-reding chapter 1 (introduction)

\usepackage{texments}
%%% for movies by alectryon
\usepackage{movies/snippets/assets/alectryon}
\usepackage{movies/snippets/assets/pygments}

@@

Let us underline the analogy between hydra battles and interactive theorem proving. Hercules is the user (you!), and hydra's heads are the subgoals: you may think that applying a tactic would solve a subgoal, but it results often in the multiplication of such tasks.

@@

Answers from \coq{} (including subgoals, error messages, etc.) are displayed in slanted style
with a different background color.

>>>>

\usepackage{texments}
%%% for movies by alectryon
\usepackage{movies/snippets/assets/alectryon}
\usepackage{movies/snippets/assets/tango_subtle}

@@

Let us underline the analogy between hydra battles and interactive theorem proving. Hercules is the user (you!), and hydra's heads are the sub-goals: you may think that applying a tactic would solve a sub-goal, but it results often in the multiplication of such tasks.

@@

Answers from \coq{} (including sub-goals, error messages, etc.) are displayed in slanted style
with a different background color.
